PAPER TEMPLATE FOR ISMIR 2014

### 2014-04-29 paper/paper.tex

@@

>>>>

\subsection{Pattern Discovery}

This recent MIREX task aims to evaluate algorithms that identify musical patterns (i.e. short fragments or melodic ideas that repeat at least twice) both from audio and symbolic representations.
Given the novelty of this task, the metrics used in 2013 (the first year to appear on MIREX) are subject to modifications in further editions.
However, Colins\cite{TomColins2013} put together all the previously existent metrics and a few new ones for this task in its first appearance in MIREX, which resulted in 21 different scores, each one implemented in MIR-eval.

@@

\subsection{Blind Source Separation}
